Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
Work on map-agreement.

A map-agreement algorithm exposes the input action $propose\left( c, deps \right)$

>>>>

A map-agreement algorithm exposes the input actions $propose\left( c, deps \right)^p$ and the output actions $decide\left( c, deps \right)^p$, for a command $c$, a set of commands $deps$, and a process $p$.
Moreover, a map-agreement algorithm must ensure that 
\begin{itemize}[noitemsep,nolistsep]
    \item test
\end{itemize}
